\large \bf Predicting Query Execution Time

### 2015-11-24 draft.tex
syncing with lab's content

	In this work, we utilize learning based models and prediction techniques which are promising reasonable accuracies in recent work \cite{ganapathi,MSR,ICDE2012}

@@

	Hypothesis testing and confidence interval estimations are two common
techniques for determining predictive accuracy \cite{forecasting}. As mentioned, 
it is not possible to estimate a priori what model would be
most predictive for a given data set without training/testing it. In this work, we are using
disjoint training and testing datasets that are generated from \textit{qgen} tool of TPC-H workload 		\cite{TPCH}. For quantifying the quality of predictions, we are using the metric called \textit{mean relative error}(MRE).
	\begin{center}
	MRE  = $\dfrac{1}{n} \sum\limits_{i=1}^n \dfrac{\left| Actual_{i} - Estimated_{i} \right|}{Actual_{i}}$
	\end{center}

>>>>

	In this work, we utilize learning based models and prediction techniques which are promising reasonable accuracies in recent work \cite{ICDE2012,MSR,ganapathi}

@@

	Hypothesis testing and confidence interval estimations are two common
techniques for determining predictive accuracy. As mentioned, 
it is not possible to estimate a priori what model would be
most predictive for a given data set without training/testing it. In this work, we are using
disjoint training and testing datasets that are generated from \textit{qgen} tool of TPC-H workload 		\cite{TPCH}. For quantifying the quality of predictions, we are using the metric called \textit{mean relative error}(MRE).
	\begin{center}
	MRE  = $\dfrac{1}{n} \sum\limits_{i=1}^n \dfrac{\left| Actual_{i} - Estimated_{i} \right|}{Actual_{i}}$
	\end{center}
